### 2019-01-21 journal/experiments.tex
coverage and placholder

\begin{figure}                                                %
{\scriptsize                                                  %
\begin{code}                                                  %
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
...                                                           %
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
<         \} else \{                                          %
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
<         \}                                                  %
...                                                           %
<                   a->avail = (jsuword)sp;                   %
<               \}                                            %
...                                                           %
---                                                           %
>         RESTORE\_SP(fp);                                    %
...                                                           %
{\bf Mutant information:}                                     %
Failure repaired by 148 mutants.                              %
...                                                           %
\#3: delete statement mutant of jsinterp.c:944:               %
                                                              %
            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
        \} else \{                                            %
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
        \}                                                    %

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */                                                            %
\end{code}                                                    %
}                                                             %
\caption{Patch and explanation for fault 115}                 %
%\vspace{-0.18in}                                             %
\label{fig:explain}                                           %
\end{figure}                                                  %

@@

>>>>

\begin{figure}                                                
{\scriptsize

\begin{code}                                                  
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} 
...                                                           
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               
<         \} else \{                                          
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    
<         \}                                                  
...                                                           
<                   a->avail = (jsuword)sp;                   
<               \}                                            
...                                                           
---                                                           
>         RESTORE\_SP(fp);                                    
...                                                           
{\bf Mutant information:}                                     
Failure repaired by 148 mutants.                              
...                                                           
\#3: delete statement mutant of jsinterp.c:944:

            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 
        \} else \{                                            
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    
        \}

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */                                                            
\end{code}                                                    
}
\caption{Patch and explanation for fault 115}                 
%\vspace{-0.18in}                                             
\label{fig:explain}                                           
\end{figure}

@@

\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c|c|}
\hline
& \multicolumn{2}{|c|}{Localization Rank} \\
\hline
Fault & Coverage & Repair \\
\hline
880 & 2,255 & - \\
95 & 720 & - \\
1294 & 190 & 1 \\
60 &  - & - \\
1543 & 18 & 19 \\
1172 & 46 & 28 \\
1561 & - & - \\
115 & 6 & 3 \\
\hline
\end{tabular}
}
\caption{Coverage localization results for SpiderMonkey}
%\vspace{-0.2in}
\label{covjstable}
\end{table}

\begin{table}
\centering
{\scriptsize
\begin{tabular}{|c||c|c|}
\hline
& \multicolumn{2}{|c|}{Localization Rank} \\
\hline
Fault &Coverage & Repair \\
\hline
139094 & 44,561 & - \\
133004 & 75 & 1 \\
158782 & - & - \\
156496 & 3,067 & - \\
143677 & 186 & - \\
158555 & 490 & - \\
134321 & - & - \\
133940 & 260 & 4 \\
141195 & 465 & - \\
156795 & 19 & - \\
139709 & 43,903 & 10 \\
155698 & 85 & 1 \\
138646 & 2 & - \\
140795 & 302 & 34 \\
136501 & 223 & 5\\
134322 & 639 & - \\
\hline
\end{tabular}
}
\caption{Coverage localization results for GCC}
\label{covgcctable}
\end{table}
